\documentclass[useAMS, usenatbib, a4paper]{mnras}
\pdfsuppresswarningpagegroup=1

\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{siunitx}
\sisetup{separate-uncertainty = true}
\usepackage{color}
\usepackage{enumerate}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{xr-hyper}
\usepackage{hyperref}

\usepackage[T1]{fontenc} 
\usepackage[utf8]{inputenc}

% Fonts 
\usepackage{newtxtext}
% Note: newtxmath must come AFTER newtxtext
\usepackage[varvw,smallerops]{newtxmath}

\usepackage{chemgreek}
\activatechemgreekmapping{newtx}
\usepackage{listings}

\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

\usepackage{etoolbox}
\robustify\bfseries
\robustify\itshape

%% The following hack solves a problem with
%% ERROR: \pdfendlink ended up in different nesting level than \pdfstartlink.
%% See https://tex.stackexchange.com/a/249743
\makeatletter
\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
  \errmessage{\noexpand\@combinedblfloats could not be patched}%
}%
\makeatother

%% Bold italic
\newcommand\hmmax{0}            % we don't need heavy fonts
\newcommand\bmmax{1}            % reduce use of math alphabets for bold
\usepackage{bm}

%% Bundled custom packages
\usepackage{aastex-compat}

\title
{Bow shocks, bow waves, and dust waves. II. Beyond the rip point}

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Henney \& Arthur]{
  William J. Henney \& S. J. Arthur\\
  \AddressCRyA
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2019}

\input{bs-bw-dw-defs.tex}

\externaldocument[Q-]{quadrics-bowshock}
%\externaldocument[I-]{bs-bw-dw-01}
%\externaldocument[III-]{bs-bw-dw-03}

\defcitealias{Tarango-Yong:2018a}{Paper~I}
\newcommand\PaperI{\citetalias{Tarango-Yong:2018a}}


\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Dust waves are a result of gas--grain decoupling in a stream of
  dusty plasma that flows past a luminous star.  The radiation field
  is sufficiently strong to overcome the collisional coupling between
  grains and gas at a \textit{rip-point}, where the ratio of radiation
  pressure to gas pressure exceeds a critical value of roughly 1000.
  When the rip point occurs outside the hydrodynamic bow shock, a
  separate dust wave may form, decoupled from the gas shell, which can
  either be drag-confined or inertia-confined, depending on the stream
  density and relative velocity.  In the drag-confined case, there is
  a minimum stream velocity of roughly \SI{60}{km.s^{-1}} that allows
  a steady-state stagnant drift solution for the dust wave apex.  For
  lower relative velocities, the dust dynamics close to the axis
  exhibit a limit cycle behavior (rip and snap back) between two
  different radii.  Strong coupling of charged grains to the plasma's
  magnetic field can modify these effects, but for a quasi-parallel
  field orientation the results are qualitatively similar to the
  non-magnetic case. For a quasi-perpendicular field, on the other
  hand, the formation of a decoupled dust wave is strongly suppressed.
\end{abstract}

\begin{keywords}
  circumstellar matter -- radiation: dynamics -- stars: winds, outflows
\end{keywords}


\section{Introduction}
\label{sec:rip-introduction}
Stellar bow shocks are predicted to occur whenever a star moves
supersonically relative to its surrounding medium, which may either be
due to the star's own motion \citetext{runaways, e.g.,
  \citealp{Blaauw:1961a}}, or due to an independent environmental flow
\citetext{weather vanes, e.g., \citealp{Povich:2008a}}.  Bow shocks
are associated with a large variety of different types of stars, for
example: AGB stars and red super-giants \citep{Cox:2012a}; OB stars
\citep{Kobulnicky:2017a}; T~Tauri stars \citep{Gull:1979a,
  Henney:2013a}; photoevaporating protoplanetary disks
\citep{Garcia-Arredondo:2001a, Smith:2005a}; neutron stars
\citep{Cordes:1993a, Brownsberger:2014a}; planetary nebula halos
\citep{Ali:2012a}; and Galactic Center sources \citep{Geballe:2004a,
  Sanchez-Bermudez:2014a}.  The dominant emission mechanism can vary
considerably between the different classes of sources, but
recombination line radiation such as H\(\alpha\), infrared continuum
radiation from warm dust, and free-free radio continuum are common
\citep{Canto:2005a, Acreman:2016a, Meyer:2016a}.  In nearly all cases,
stellar bow shocks are easily spatially resolved and mapped, allowing
their shapes to be compared with theoretical predictions
\citep{Wilkin:1996a, Tarango-Yong:2018a}.  A different class of
stellar bow shocks are found in interacting binary systems
\citep{Stevens:1992a}, but these typically emit by non-thermal
mechanisms and are only resolvable using radio interferometry
techniques \citep{Contreras:1999a, Dzib:2013a}.

In \citet{Henney:2019a} (hereafter, Paper~I) we studied the formation
of bows around OB stars by the combined action of their winds and
radiation.  For the case of strong collisional coupling between gas
and dust grains, we showed that three different regimes of interaction
are possible, according to the relative values of stellar wind
radiative momentum efficiency \(\eta\wind\) and the UV optical depth of
the bow shell \(\tau\):
\begin{enumerate}[{\(\star\)}]
\item Wind-supported bow shocks (WBS) where \(\tau < \eta\wind\).  These are
  purely hydrodynamic (or MHD) interactions, in which the stellar
  radiation is dynamically unimportant.  This regime dominates for
  fast-moving stars and for low-density environments.
\item Radiation-supported bow waves (RBW) where
  \(\eta\wind < \tau < 1\).  In these optically thin bows, the stellar
  radiative momentum gradually decelerates the oncoming stream in a
  broad shell.  This regime is important for B~stars and weak-wind
  O~stars in moderate density environments (\(> \SI{100}{cm^{-3}}\)).
\item Radiation-supported bow shocks (RBS) where \(\tau > 1\).  These are
  optically thick shells, internally supported by the trapped stellar
  radiation pressure.  This regime applies to slow-moving O~stars in
  dense environments.
\end{enumerate}
In this paper, we investigate under what circumstances the strong
gas--grain coupling might break down, leading to a fourth regime: a
separate dust wave outside of the hydrodynamic bow shock (see Fig.~1
of Paper~I).

In neutral and molecular regions, the drag forces are relatively weak
and so divergent dynamics of gas and grains are frequently found in
the context of molecular clouds \citetext{\citealp{Hopkins:2016a,
    Lee:2017a, Mattsson:2019a}, but see \citealp{Tricco:2017a}} and
protoplanetary disks \citep{Weidenschilling:1977b, Birnstiel:2010a,
  Dipierro:2018a}.  In ionized regions, the electrostatic forces
between charged dust grains and charged gas particles (principally
protons) leads to greatly increased drag forces, which tend to
maintain a tight coupling between dust and gas \citep{Draine:2011a}.
However, in a photoionized \hii{} region around a high-mass star, the
dust feels a much larger radiation force than does the gas. This leads
to a slow relative drift between the two components in the outer
regions of the nebula \citep{Gail:1979a, Akimkin:2015a, Akimkin:2017a,
  Ishiki:2018a} and a total decoupling very close to the central star
\citep[Fig.~8 of][]{Draine:2011a}.

With respect to stellar bow shocks, gas--grain decoupling has been
previously studied in the context of post-shock flow, where it is the
sudden deceleration of the gas that is the primary impetus for the
dust to separate.  The case of a cool red supergiant was simulated by
\citet{van-Marle:2011a}, where large grains present in the stellar
wind are not stopped in the inner termination shock, but are carried
through the contact discontinuity by their inertia, penetrating into
the interstellar medium.  \citet{Katushkina:2017a} simulated the
opposite case, where grains in the ambient medium become decoupled
from the gas after passing the outer bow shock, and subsequently
gyrate about the magnetic field, forming filamentary structures (see
also \citealp{Katushkina:2018a}).  In this paper, we study a different
decoupling mechanism, where it is the stellar radiation force acting
on the grains that causes a separation from the gas \emph{before the
  stream reaches the bow shock}.  This mechanism was first proposed by
\citet{Ochsendorf:2014b} to explain the infrared emission arc around
the high-mass multiple system \(\sigma\)~Ori.

The plan of the paper is as follows.
%
In \S~\ref{sec:recap-paper-i} we give some results from Paper~I that
we will need in later sections.
%
In \S~\ref{sec:gas-free-bow} we calculate analytical models of the
shape of dust waves in the drag-free limit.
% %
% In \S\ref{sec:cloudy-models-dust} we discuss the relevant dust physics
% and the Cloudy models that we employ.
%
In \S~\ref{sec:imperf-coupl-betw} we calculate in detail the grain
charging and dynamics, subject to radiation and drag forces, in order
to determine the \textit{rip point}, which is where gas--grain coupling
catastrophically breaks down.  This is used to determine existence
conditions for the presence of a decoupled dust wave.
%
In \S~\ref{sec:magn-effects-grain} we consider the coupling between
the grains and the plasma's magnetic field, and how this effects the
existence and structure of dust waves.
%
In \S~\ref{sec:discussion} we discuss our results in the context of
previous studies.
%
In \S~\ref{sec:summary} we summarise our findings.
%
In Appendix~\ref{sec:equat-moti-grains} we provide additional
technical information on the numerical calculation of grain
trajectories.

\section{Recapitulation of Paper~I}
\label{sec:recap-paper-i}

In Paper~I, we found approximate expressions for the bow radius in each of the three regimes discussed in the introduction: 
%% XREF \ref{eq:x-cases}
\begin{equation}
\begin{aligned}
  \text{RBS} \quad& (\tau_*^2 > 1): & R_0 &\approx  (1 + \eta\wind)^{1/2} \, R_*  \\
  \text{RBW} \quad& (\eta\wind < \tau_*^2 < 1): & R_0 &\approx 2 \, \tau_* \, R_* \\
  \text{WBS} \quad& (\tau_*^2 < \eta): & R_0 &\approx \eta\wind^{1/2} \, R_*  
\end{aligned}\label{eq:x-cases}
\end{equation}
In these expressions, we use a fiducial radius
%% XREF \eqref{eq:Rstar}
\begin{equation}
  \label{eq:Rstar}
  R_* = \left(\frac{L}{4\pi c \rho v_\infty^2}\right)^{1/2} \ ,
\end{equation}
a fiducial optical depth
%% XREF \eqref{eq:tau-star},
\begin{equation}
  \label{eq:tau-star}
  \tau_* = \rho \kappa R_* \ ,
\end{equation}
and a factor that describes the efficiency of the stellar wind as the fraction of the stellar radiation momentum that is converted to wind momentum
\begin{equation}
  \label{eq:wind-efficiency}
  \eta\wind  = \frac{c\, \dot{M} V\wind}{L} \ .
\end{equation}
Paper~I's equation~(11) allows a more exact value for \(R_0\) to be
found numerically in intermediate cases.  Note that \(R_0\) is the
star--apex distance measured along the symmetry axis of the bow
\citetext{see \citealp{Tarango-Yong:2018a} for explanation of
  nomenclature and discussion of bow shapes}, and is calculated in the
limit that the momentum transfer occurs at a surface.  In cases where
the shell's finite width is significant, \(R_0\), should correspond
approximately to the astropause (contact discontinuity) in the WBS
regime, or a UV optical depth of unity (as measured from the star) in
the RBS regime.  The total perpendicular optical depth of the shell to
stellar radiation can be found as
\begin{equation}
  \label{eq:actual-tau}
  \tau = \frac{R_0}{R_*} \, \tau_* \ .
\end{equation}

In the foregoing, we employ the stellar bolometric luminosity, \(L\),
wind mass-loss rate, \(\dot{M}\), and terminal velocity, \(V\wind\),
together with the ambient stream's mass density, \(\rho\), relative
velocity \(v_\infty\), and effective dust opacity, \(\kappa\).  It is convenient
to define dimensionless versions of these parameters by normalizing to
typical values:
\begin{align*}
  % \label{eq:stellar-parameters}
  \dot{M}_{-7} &= \dot{M} / \bigl(\SI{e-7}{M_\odot.yr^{-1}}\bigr) \\
  V_3 &= V / \bigl(\SI{1000}{km.s^{-1}}\bigr) \\
  L_4 &= L / \bigl(\SI{e4}{L_\odot}\bigr) \\
  v_{10} &= v_\infty / \bigl( \SI{10}{km.s^{-1}} \bigr) \\
  n &= (\rho / \bar{m}) / \bigl( \SI{1}{cm^{-3}} \bigr) \\
  \kappa_{600} &= \kappa / \bigl( \SI{600}{cm^2.g^{-1}} \bigr) \ ,
\end{align*}
where \(\bar{m}\) is the mean mass per hydrogen nucleon
(\(\bar{m} \approx 1.3 m_{\text{p}} \approx \SI{2.17e-24}{g}\) for solar
abundances).  In terms of these dimensionless parameters,
equations~(\ref{eq:Rstar}--\ref{eq:wind-efficiency}) take the
convenient forms:
%% XREF \ref{eq:wind-eta-typical}
%% XREF \ref{eq:taustar-typical}
%% XREF \ref{eq:Rstar-typical}
\begin{align}
  \label{eq:Rstar-typical}
  R_* / \si{pc} &= \num{2.21} \, (L_4 / n)^{1/2} \,v_{10}^{-1} \\
  \label{eq:taustar-typical}
  \tau_* &= \num{0.0089} \,\kappa_{600} \, (L_4 \,n)^{1/2} \,v_{10}^{-1} \\
  \label{eq:wind-eta-typical}
  \eta\wind &= \num{0.495} \,\dot{M}_{-7} \,V_3  \,L_4^{-1} \ .
\end{align}


\input{app-dust-wave}

\input{sec-weak-coupling}

\input{sec-dust-wave-discussion}

\section*{Acknowledgements}
We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grants Programa de Apoyo a Proyectos de Investigación
e Inovación Tecnológica IN112816 and IN107019.  This work has made
extensive use of Python language libraries from the SciPy
\citep{Jones:2001a} and AstroPy \citep{Astropy-Collaboration:2013a,
  Astropy-Collaboration:2018a} projects.  We thank Olga Katushkina for useful discussions. 


\bibliographystyle{mnras}
\bibliography{bowshocks-biblio}
\appendix
\input{app-dust-equations}

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
