\documentclass[useAMS, usenatbib, a4paper]{mnras}
\pdfsuppresswarningpagegroup=1

\usepackage{graphicx}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{fixltx2e}
\usepackage{booktabs}
\usepackage{siunitx}
\sisetup{separate-uncertainty = true}
\usepackage{color}
\usepackage{enumerate}
\usepackage{pdflscape}
\usepackage{rotating}
\usepackage{xr-hyper}
\usepackage{hyperref}

\usepackage[T1]{fontenc} 
\usepackage[utf8]{inputenc}

% Fonts 
\usepackage{newtxtext}
% Note: newtxmath must come AFTER newtxtext
\usepackage[varvw,smallerops]{newtxmath}

\usepackage{chemgreek}
\activatechemgreekmapping{newtx}
\usepackage{listings}

\hypersetup{colorlinks=True, linkcolor=blue!50!black, citecolor=black,
  urlcolor=blue!50!black}

\usepackage{etoolbox}
\robustify\bfseries
\robustify\itshape

%% The following hack solves a problem with
%% ERROR: \pdfendlink ended up in different nesting level than \pdfstartlink.
%% See https://tex.stackexchange.com/a/249743
\makeatletter
\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
  \errmessage{\noexpand\@combinedblfloats could not be patched}%
}%
\makeatother

%% Bold italic
\newcommand\hmmax{0}            % we don't need heavy fonts
\newcommand\bmmax{1}            % reduce use of math alphabets for bold
\usepackage{bm}

%% Bundled custom packages
\usepackage{aastex-compat}

\title
{Bow shocks, bow waves, and dust waves. III. Diagnostics}

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Henney \& Arthur]{
  William J. Henney\thanks{w.henney@irya.unam.mx}
  \& S. J. Arthur\\
  \AddressCRyA
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2019}

\input{bs-bw-dw-defs.tex}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Stellar bow shocks, bow waves, and dust waves all result from the
  action of a star's wind and radiation pressure on a stream of dusty
  plasma that flows past it.  The dust in these bows emits prominently
  at mid-infrared wavelengths in the range \SIrange{8}{60}{\um}. We
  propose a novel diagnostic method, the \(\tau\)--\(\eta\) diagram,
  for analyzing these bows, which is based on comparing the fractions
  of stellar radiative energy and stellar radiative momentum that is
  trapped by the bow shell.  This diagram allows the discrimination of
  wind-supported bow shocks, radiation-supported bow waves, and dust
  waves in which grains decouple from the gas.  For the wind-supported
  bow shocks, it allows the stellar wind mass-loss rate to be
  determined.  We critically compare our method with a previous method
  that has been proposed for determining wind mass-loss rates from bow
  shock observations. This comparison points to ways in which both
  methods can be improved and suggests a downward revision by a factor
  of two with respect to previously reported mass-loss rates.  From a
  sample of 23 mid-infrared bow-shaped sources, we identify at least 4
  strong candidates for radiation-supported bow waves, which need to
  be confirmed by more detailed studies, but no strong candidates for
  dust waves.
\end{abstract}

\begin{keywords}
  circumstellar matter -- radiation: dynamics -- stars: winds, outflows
\end{keywords}

\section{Introduction}
\label{sec:introduction}

Bow-shaped circumstellar nebulae are observed around a wide variety of
stars \citep{Gull:1979a, Cox:2012a, Cordes:1993a} but are most
numerous around luminous OB stars \citep{Kobulnicky:2016a}.  They are
most commonly interpreted as bow shocks, due to a supersonic relative
motion of the surrounding medium, which interacts with the stellar
wind \citep{Wilkin:1996a}.  Early surveys for bow shocks around OB
stars \citep{van-Buren:1995a} concentrated on runaway stars
\citep{Blaauw:1961a, Hoogerwerf:2001a} that have been ejected at high
velocities (\(> \SI{30}{km.s^{-1}}\)) due to multi-body encounters in
star clusters or due to the core-collapse supernova explosion of a
binary companion.  However, only a small fraction of runaways show
detectable bow shocks \citep{Huthoff:2002a, Peri:2012a, Peri:2015a,
  Prisegen:2019a}. Targeted searches at mid-infrared wavelengths of
particular high-mass star forming regions such as M17 and RCW~49
\citep{Povich:2008a}, Cygnus~X \citep{Kobulnicky:2010a}, and Carina
\citep{Sexton:2015b} have revealed many bows around slower moving
stars.  In many cases, it may be streaming motions in the interstellar
medium that provide most of the relative velocity: weather vanes
rather than runaways \citep{Povich:2008a}.  More recently, large-scale
surveys of the Galactic Plane \citep{Kobulnicky:2016a,
  Kobulnicky:2017a} and of nearby stars in the Bright Star Catalog
\citep{Bodensteiner:2018a} have revealed hundreds more such bow shocks.

Analytic and semi-analytic thin-shell models of bow shocks have been
developed \citep{van-Buren:1992a, Wilkin:1996a, Canto:1996},
including the effects of non-spherical winds and nonaxisymmetric bows
\citep{Wilkin:2000a, Henney:2002a, Canto:2005a, Tarango-Yong:2018a}.
Increasingly realistic numerical hydrodynamic simulations have been
performed \citep{Matsuda:1989a, Raga:1997a, Comeron:1998a,
  Meyer:2014b, Mackey:2015a}, including magnetic fields
\citep{Meyer:2017a, Katushkina:2017a, Katushkina:2018a} and detailed
predictions of the dust emission \citep{Meyer:2016a, Acreman:2016a,
  Mackey:2016a}.

% Despite the almost
% universal use of the term ``bow shock'' to describe these objects, it
% may be that slow subsonic velocities of a star through its \hii{}
% region are sufficient \citep{Mackey:2015a, Mackey:2016a} to distort
% the inner stellar wind shock and produce a bow appearance to the
% mid-infrared emission, even though there is no shock in the dusty
% ambient stream.

In \citet[Paper~I and Paper~II]{Henney:2019a, Henney:2019b} we
presented a taxonomy of stellar bows, which we divided into
wind-supported bow shocks (WBS) and various classes of
radiation-supported bows.  When the dust and gas remains well-coupled
(Paper~I), these are optically thin radiation-supported bow waves
(RBW) and optically thick radiation-supported bow shocks (RBS).  When
the dust decouples from the gas (Paper~II), inertia-confined dust
waves (IDW) and drag-confined dust waves (DDW) can result.

In Paper~I we derived expressions for the bow radius \(R_0\) in each of
the three well-coupled regimes as a function of the parameters of the
star and the ambient medium.  In Paper~II, we found the criteria for
the dust to decouple from the gas to form a separate dust wave outside
of the hydrodynamic bow shock.  The most important of these is that
the ratio of radiation pressure to gas pressure should exceed a
critical value, \(\Xi_\dag \sim 1000\).  

In order to provide an empirical anchor to our theoretical
calculations, we now consider how the parameters of our models might
be determined from observations.  The parameter-space diagrams, such
as Figure~2 of Paper~I, are not always useful in this regard, since in
many cases the ambient density and relative stellar velocity are not
directly measured.  Instead, we aim to construct diagnostics based on
the most common observations, which are of the infrared dust emission.
Key questions that we wish to address include
\begin{enumerate}[1.]
\item Can we distinguish observationally between radiation support
  (bow waves and dust waves) and wind support (bow shocks)?
\item Are there any clear examples of sources with radiation-supported bows?
\item In the case of wind support, can we reliably determine mass loss
  rates from mid-infrared observations?
\end{enumerate}

The outline of the paper is as follows. In
\S~\ref{sec:energy-trapp-vers} we describe how the optical depth and
the gas pressure in the bow shell can be estimated from a small number
of observed quantities.  In \S~\ref{sec:eta-tau-diagnostic} we place
observed bow sources on a diagnostic diagram of these two quantities
and discuss the influence of observational errors and systematic model
uncertainties. In \S~\ref{sec:cand-radi-supp} we use the diagram to
identify some candidates for radiation-supported bows. In
\S~\ref{sec:grain-temp-emiss} we calculate the grain emissivity as a
function of the stellar radiation field around OB stars.  In
\S~\ref{sec:stellar-wind-mass} we compare two different methods of
estimating the stellar wind mass loss rates from observations of the
bows. In \S~\ref{sec:discussion} we discuss various groups of bows
that require special treatment due to their diverse physical
conditions. In \S~\ref{sec:conclusions} we summarise out findings.

\input{sec-observational-diagnostics}



\section{Summary}
\label{sec:conclusions}

We have proposed a novel diagnostic method, the \(\tau\)-\(\eta\shell\)
diagram, for analyzing observations of stellar bow shocks around OB
stars, which allows discrimination between radiation-supported and
wind-supported bows.  Our principal results are as follows:
\begin{enumerate}[1.]
\item The UV optical depth \(\tau\) of the bow shell can be estimated
  from the observed infrared shell luminosity \(L\IR\) and stellar
  luminosity \(L_*\) as \(\tau = 2 L\IR/L_*\)
  (\S~\ref{sec:energy-trapp-vers}).
\item The shell momentum efficiency \(\eta\shell\), which is the
  fraction of stellar radiative momentum that is transferred to the
  shell either directly or indirectly (via stellar wind), can be
  estimated from \(\tau\) and the observed shell radius \(R_0\), after
  making some auxiliary assumptions about the physical conditions in
  the shell (\S~\ref{sec:energy-trapp-vers}).
\item By comparing \(\tau\) and \(\eta\shell\), it is possible to
  discriminate between three regimes (\S~\ref{sec:eta-tau-diagnostic}
  and see Paper~I): wind-supported bow shocks
  (\(\eta\shell \gg \tau\)), radiation-supported bow waves
  (\(\eta\shell \sim \tau < 1\)), and radiation-supported bow shocks
  (\(\eta\shell \sim \tau > 1\)).
\item Shells with \(\eta\shell < \num{e-3}\) are potentially in a
  fourth regime of dust waves, where gas--grain collisional coupling
  breaks down (see Paper~II).
\item By analyzing a published sample of 20 mid-infrared bow shock
  candidates \citep[K18]{Kobulnicky:2018a}, plus additional compact
  bows in Orion, we find 4 strong candidates for radiation-supported
  bow waves plus 3 marginal cases (\S\S~\ref{sec:cand-radi-supp} and
  \ref{sec:comm-prop-cand}).  No strong candidates for dust waves are
  found.
\item For wind-supported bow shocks, the stellar wind mass-loss rate
  can be found from \(\tau\) and \(\eta\shell\)
  (\S~\ref{sec:mass-loss-determ}). We compare this method with the
  previously proposed method of K18 (\S~\ref{app:bow-shock-data}) and
  suggest a correction to the dust emissivities used in the latter,
  which reduces the mass-loss rates by a factor of about 2.
\item After this correction, the two mass-loss methods agree well for
  small bows (\(R_0 \le \SI{0.3}{pc}\)), but the
  \(\tau\)--\(\eta\shell\) method under-predicts the mass-loss rate by
  up to a factor of 10 for larger bows, which also tend to have
  relatively thin shells (\S~\ref{sec:underst-diff-betw}).  This
  discrepancy could be eliminated by extending the
  \(\tau\)--\(\eta\shell\) method to include the observed shell
  thickness.
\item Disruption of the largest dust grains by rotational torques in
  the strong circumstellar radiation field is predicted to have a
  relatively modest effect on the optical properties of the dust
  mixture (\S~\ref{sec:evolution-grain-size}), increasing the UV
  opacity by about 50\%.
\end{enumerate}


\section*{Acknowledgements}
We are grateful for financial support provided by Dirección General de
Asuntos del Personal Académico, Universidad Nacional Autónoma de
México, through grant Programa de Apoyo a Proyectos de Investigación e
Inovación Tecnológica IN107019.  This work has made extensive use of
Python language libraries from the SciPy \citep{Jones:2001a}, AstroPy
\citep{Astropy-Collaboration:2013a, Astropy-Collaboration:2018a} and
Pandas \citep{McKinney:2010a} projects.  We thank Chip Kobulnicky for
sharing results in advance of publication.



\bibliographystyle{mnras}
\bibliography{bowshocks-biblio}
\appendix
\input{app-k17-k18}

% \section{Notes on particular sources}

\section{The Herbig Be star V750~Mon}
\label{sec:notes-part-sourc}
\label{sec:hd-53367-v750}
  
K18 source~380 (HD~53367, V750~Mon) is a Herbig Be star with spectral
type B0V--B0III and mass 12 to \SI{15}{M_\odot}, which shows
long-scale irregular photometric variability \citep{Tjin-A-Djie:2001a,
  Pogodin:2006a} together with cyclic radial velocity variations,
which are interpreted as an eccentric binary with a \SI{5}{M_\odot}
pre-main-sequence companion.  It is located outside the solar circle
and, although it was originally classified as part of the CMa OB
association at about \SI{1}{kpc} \citep{Tjin-A-Djie:2001a}, more
recent estimates put it much closer.  K18 assume a distance of
\SI{260}{pc}, based on Hipparcos measurements
\citep{van-Leeuwen:2007a}, but its Gaia DR2 parallax
\citep{Gaia-Collaboration:2016a, Gaia-Collaboration:2018a, Luri:2018a}
puts it closer still at \SI{140 \pm 30}{pc}.  This is the median and
90\% confidence interval, estimated from Bayesian
inference\footnote{\url{https://github.com/agabrown/astrometry-inference-tutorials/}.}
using an exponential density distribution with scale length of
\SI{1350}{pc} as a prior.

\citet{Quireza:2006b} report a kinematic distance to the associated
\hii{} region IC~2177 (G\num{223.70}\num{-1.90}) of \SI{1.6}{kpc},
based an LSR radio recombination line velocity of \SI{+16}{km.s^{-1}}
\citep{Quireza:2006a} and the outer Galaxy rotation curve of
\citet{Brand:1993a}.  However, given the dispersion in peculiar
velocities of star-forming clouds (\SIrange{7}{9}{km.s^{-1}},
\citealp{Stark:1984a}) and likely streaming motions of the ionized gas
(\(\approx \SI{10}{km.s^{-1}}\), \citealp{Matzner:2002a, Lee:2012a}),
this is still consistent with a much smaller distance, which would
also help in bringing the radio continuum-derived nebular electron
density into agreement with the value (\(\approx \SI{100}{cm^{-3}}\))
derived from the optical [\ion{S}{ii}] line ratio
\citep{Hawley:1978a}.

\citet{Fairlamb:2015a} derive a distance of \SI{340 \pm 60}{pc} from
combining a spectroscopically determined effective temperature,
gravity, and reddening with photometry and pre-main sequence
evolutionary tracks.  They also determine a luminosity of \SI{13000
  \pm 1000}{L_\odot}, which is only half that assumed by K18, and
would have to be even lower to bring the photometry into concordance
with the Gaia distance.  Alternatively, the luminosity could remain
the same if the total-to-selective extinction ratio were higher than
the \(R_V = 3.1\) assumed by \citet{Fairlamb:2015a}.  Taking
\(R_V = 5.5\) instead, as in Orion, would give \(A_V = 3.34\) and a
predicted \(V\) magnitude of 6.7 if we assume \(L_4 = 1.3\),
\(D = \SI{170}{pc}\) (furthest distance in Gaia 90\% confidence
interval) and \(T_{\text{eff}} = \SI{29.5}{kK}\)
\citep{Fairlamb:2015a} for a bolometric correction of \(-2.86\)
\citep{Nieva:2013a}.  The observed brightness varies between
\(V = 6.9\) and 7.2, which is still at least 20\% fainter than
predicted, but this is the best that can be achieved without rejecting
the Gaia parallax distance entirely.

A final sanity check can be performed by considering the free-free
radio continuum flux of V750~Mon's surrounding \hii{} region, which,
after converting to a luminosity, should be proportional to the total
recombination rate in the nebula and therefore, assuming
photoionization equilibrium and negligible dust absorption in the
ionized gas, also proportional to the ionizing photon luminosity of
the star.  \citet{Quireza:2006b} report a flux density of \SI{6}{Jy}
at \SI{8.6}{Ghz} for G\num{223.70}\num{-1.90}, as compared with a flux
density of \SI{260}{Jy} for the Orion Nebula using the same
instrumental setup.  Assuming an ionizing photon luminosity of
\(S_{49} = 1\) and distance \SI{410}{pc} for the ionizing Trapezium
stars in Orion, therefore implies
\(S_{49} = 0.0027 (D/\SI{140}{pc})^2\) for V750~Mon.  Using an
ionizing flux of \SI{3.2e22}{cm^{-2}.s^{-1}} from the curves in Fig.~4
of \citet{Sternberg:2003a}, this translates to a bolometric luminosity
of \(L_4 = 0.96 (D/\SI{140}{pc})^2\), which is consistent with the
\citet{Fairlamb:2015a} value if we take a distance towards the high
end of the Gaia range.

% \subsection{Source 407, HD~93249}
% \label{sec:source-407}

% TODO

% \subsection{Source 342}
% \label{sec:source-342}

% Source~342 is anomalous in both methods. Has high mass loss for low luminosity.


% \subsection{Source 344}
% \label{sec:source-344}

% This has big disagreement between K18 and me.  My mass-loss rate seems too low, given its high luminosity. Why?



% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
